Median Maximum Pairwise Distance

### 2020-08-20 main.Rmd
title and subtitles changed

# Initial distribution of observed variables shown in plot title

@@

## Algorithm

@@

### Interpreting the test statistic

@@

## Algorithm for threshold

@@

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```

@@

*Conclusion*: The test does not select harmony pairs when distributions of categories are same.

@@

# Behavior of the statistic - control simulation

@@

# Conclusion

>>>>

#### Initial distribution of observed variables shown in plot title

@@

## Median Maximum Pairwise distance

### Definition

### Algorithm for computation for all harmony pairs

@@

### Bounds

This is not correct becuase MMPD should be median of standardized Gumbel distribution. So no bound?

By @Lin1991-fj,
$$ 0 \leq JSD(P||Q) \leq ln(2)$$.

Thus,  $$ 0 \leq MMPD \leq \frac{ln(2)}{ln(k)}$$.
Now, by asumption $k \geq 2$ and hence,
<!-- \begin{equation} -->
<!-- For k = 2, $\frac{ln(2)}{ln(k)} = 1$  -->
<!-- \end{equation} -->
<!-- For $k > 2$, $\frac{ln(2)}{ln(k)}  <1$. -->

\[\frac{ln(2)}{ln(k)} : \left\{
  \begin{array}{lr}
    1 & if \ k = 2\\
    <1 & if \ k \ge 2
  \end{array}
\right.
\]

Thus, $$ 0 \leq MMPD \leq \ 1$$

@@

## Definition

### Algorithm for computation for all harmony pairs

@@

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```
## Simulation design

Behavior of the statistic - control simulation

@@

*Conclusion*: The test rejects the null hypothesis if distributions are different.

@@

@@

# Summary and discussion
